### 2013-07-26 paper.tex
I hate my life.

In general, a string of $s$'s and $t$'s will be referred to as an \emph{expression}.  In the case where there are no consecutive identical characters (e.g. $\AA_n$), we will refer to them as \emph{reduced expressions}.

@@

@@

First, we need a criteria to determine the top.  Fortunately, this is extremely easy.
\begin{definition*}
	For a binary string $\ul b$, let $\pi_1(\ul b)$ denote the number of $1$'s in $\ul b$, and $\pi_0(\ul b)$ the number of $0$'s.
\end{definition*}
\begin{proposition}
	For any $\ul b$ of length $n$, \[
		\Top_{\SS_n} \ul b =
		\begin{cases}
			\varnothing & \text{if } \pi_1(\ul b) \equiv 0 \pmod{2} \\
			s & \text{if } \pi_1(\ul b) \equiv 1 \pmod{2} \\
		\end{cases}.
		\]
	\label{prop:s_top}
\end{proposition}
\begin{proof}
	Straightforward induction on $n$.  
\end{proof}

@@

In this section we will show several results which show that the possible outputs of a map with base $\AA_n$ are extremely restricted.  We present them below, before providing proofs of each.
\begin{theorem}[Bubble Theorem]
	Consider a bubble in a full-diagram with base $\AA_n$.  The bubble holds exactly one caterpillar, whose color is opposite that of the bubble.
	\label{thm:bubble}
\end{theorem}
\begin{theorem}[Caterpillar Theorem]
	Any caterpillar in a full-diagram with base $\AA_n$ evaluates in the form $x^my^n\alpha_s$ if it is blue, or $x^my^n\alpha_t$ is red.
	\label{thm:caterpillar}
\end{theorem}
\begin{theorem}[Pasture Theorem]
	Consider a full-diagram with $N+1$ pastures (numbered $0$, $1$, \dots, $N$) with base $\AA_n$ and top $T$.  Suppose further that $N \ge 1$ (or equivalently, $T \neq \varnothing$).  Then:
	\begin{enumerate}[(i)]
		\ii Pastures $1$ through $N-1$ contain either nothing or an attached component.
		\ii Pasture $N$ contains nothing if $T[N] = \AA_n[n]$, and contains a single caterpillar otherwise.
	\end{enumerate}
	\label{thm:pasture}
\end{theorem}

\subsection{Proof of the Bubble Theorem}
We begin with a proof of the bubble theorem, which is the crux result of the alternating case.  Indeed, both of the subsequent theorems are fairly straightforward consequences of this theorem.

It's interesting to note that the Bubble Theorem is intuitively very natural.  The main difficulty is finding a clean way to handle the special cases generated by the convoluted geometry.

\begin{proof}[Proof of Theorem \ref{thm:bubble}]
	Take a bubble $B$ and assume without loss of generality that it is blue.  It is easy to see, by considering two anchors on the boundary of blue, that there is some red anchor inside $B$.  This implies that $B$ has at least one red caterpillar.

@@

\subsection{Proof of the Caterpillar Theorem}
We will now derive the Caterpillar Theorem as a consequence of the Bubble Theorem.

@@

	We perform induction on the size of the caterpillar. 
	If there are no bubbles, then the caterpillar is simply a barbell (because it is a tree, which contracts to a barbell).
	This is the base step.
	For the inductive step, consider an arbitrary bubble.  Inside it is exactly one caterpillar, say $c$, by the Bubble Theorem.  Because the original caterpillar has nesting level $0$, we deduce $c$ is merely a barbell, and hence is either $\alpha_s$ or $\alpha_t$.
	Applying the barbell-forcing rule of equation \eqref{eq:barbell_break} generates two terms.  One of them is zero because it creates a new empty bubble. The other is the original diagram with the cycle cut open and the contents removed, multiplied by one of $\left\{ x,y \right\}$.  The inductive hypothesis now applies directly, and this completes the first induction.

@@

		label("$\to$", (7,0));
	\end{asy}
	\caption{In the first diagram, $\ul a = \ul b = 110010$.  In the second, $\ul a' = \ul b' = 110010111$.  Closing the pastures allows us to deduce the Pasture Theorem from the Bubble Theorem.}
	\label{fig:pf_pasture}
\end{figure}
The bubble theorem and the pasture theorem are structurally very similar.  In fact, we will now show a somewhat surprising proof that the Pasture Theorem follows from the Bubble Theorem.
\begin{proof}[Proof of Theorem \ref{thm:pasture}]
	Again, let $T$ denote the top, with length $N$.  In the first case, suppose $T[N] \neq \AA_n[n]$; that is, the last characters of $T$ and $\AA_n$ differ.  Then it must be the case that the rightmost anchor is not part of a fence.
	Now suppose the map arose from $\MM_{\AA_n}(\ul a, \ul b)$.  Let $\ul a'$ be the string formed by appending $N$ $1$'s to $\ul a$, and define $\ul b'$ similarly.  Now consider the map \[ \MM_{\AA_{n+N}} \left( \ul a', \ul b' \right). \]  See figure \ref{fig:pf_pasture} for an example.

	It is easy to verify that the top of this new map is zero.  Now what we have done is enclose the contents of each pasture into bubbles.  The Bubble Theorem tells us that the innermost bubble can have exactly one caterpillar, while the other bubbles must contain only a single caterpillar, which was once a fence.  This implies the Pasture Theorem in the first case.

@@

\begin{corollary}
	For any binary strings $\ul a$ and $\ul b$ of length $n$
\end{corollary}<++>

@@

\begin{definition*}
	We say that two strings $\ul{r_1}$ and $\ul{r_2}$ \emph{agree in $c$} if their last characters are both $c$.
\end{definition*}
\begin{definition*}
	For a binary string $\ul r$, let $\ul r'$ be the string formed by deleting the last bit of $\ul r$.
\end{definition*}

\begin{proposition}
	Suppose $n \ge 1$ is an integer.  Let $\ul a$ and $\ul b$ be two binary strings of length $n$ which agree in the last bit, which have the same top $T = \Top_{\AA_n} \ul a = \Top_{\AA_n} \ul b$.  Suppose $M_1 = \MM_{\AA_{n-1}} (\ul a', \ul b') \neq 0$.  Then $M = \MM_{\AA_n} (\ul a, \ul b$) is nonzero, and the following recursion holds.
	\begin{enumerate}[(i)]
		\ii If $\AA_n$ and $T$ have the same last character $c$ (so $T \neq \varnothing$)
		\begin{itemize}
			\ii If $\ul a[n] = \ul[b] = 1$, then $M = M_1$.
			\ii If $\ul a[n] = \ul[b] = 0$, then $M = -f / \alpha_k$ where $f$ is the monomial in $M_1$ with the largest factor of $\alpha_k$, with any quantum numbers
		\end{itemize}<++>
	\end{enumerate}<++>
	\label{thm:recurse}
\end{proposition}

>>>>

In general, a string of $s$'s and $t$'s will be referred to as an \emph{expression}.  In the case where there are no consecutive identical characters (e.g. the string is either $\AA_n$ or $\AA_n'$), we will refer to them as \emph{reduced expressions}.

@@

This motivates us to make the following definition, which will be used in section \ref{sec:res_altcompute}.
\begin{definition*}
	For any reduced expression $\ul r$, we adopt the quantum polynomial $Q_{\ul r}$ by :
	\[
		Q_{\AA_n} = 
		\begin{cases}
			[n+1]_x \alpha_s + [n]_y \alpha_t & \text{if $n$ is odd} \\
			[n]_x \alpha_s + [n+1]_y \alpha_t & \text{if $n$ is even}
		\end{cases}
	\]
	when $\ul r = \AA_n$, and otherwise,
	\[
		Q_{\AA_n'} =
		\begin{cases}
			[n]_x \alpha_s + [n+1]_y \alpha_t & \text{if $n$ is even} \\
			[n+1]_x \alpha_s + [n]_y \alpha_t & \text{if $n$ is odd}
		\end{cases}.
	\]
\end{definition*}

It is easy to observe that if $\ul r$ is a reduced expression of length $n+1$, then \[ \MM_{\ul r} ( \underbrace{11\dots11}_{\text{$n$ 1's}}0, \underbrace{11\dots11}_{\text{$n$ 1's}}0 ) = Q_{\ul r}. \]

@@

First, we need a criteria to determine the top.  Fortunately, this is extremely easy.
\begin{definition*}
	For a binary string $\ul b$, let $\pi_1(\ul b)$ denote the number of $1$'s in $\ul b$, and $\pi_0(\ul b)$ the number of $0$'s.
\end{definition*}
\begin{proposition}
	For any $\ul b \in \BB_n$, \[
		\Top_{\SS_n} \ul b =
		\begin{cases}
			\varnothing & \text{if } \pi_1(\ul b) \equiv 0 \pmod{2} \\
			s & \text{if } \pi_1(\ul b) \equiv 1 \pmod{2} \\
		\end{cases}.
		\]
	\label{prop:s_top}
\end{proposition}
\begin{proof}
	Straightforward induction on $n$.  
\end{proof}

@@

In this section we will show several results which show that the possible outputs of a map with base $\AA_n$ are extremely restricted.  We present them below, before providing proofs of each.
\begin{lemma}[Bubble Lemma]
	Consider a bubble in a full-diagram with base $\AA_n$.  The bubble holds exactly one caterpillar, whose color is opposite that of the bubble.
	\label{thm:bubble}
\end{lemma}
\begin{theorem}[Caterpillar Theorem]
	Any caterpillar in a full-diagram with base $\AA_n$ evaluates in the form $x^my^n\alpha_s$ if it is blue, or $x^my^n\alpha_t$ is red.
	\label{thm:caterpillar}
\end{theorem}
\begin{theorem}[Pasture Theorem]
	Consider a full-diagram with $N+1$ pastures (numbered $0$, $1$, \dots, $N$) with base $\AA_n$ and top $T$.  Suppose further that $N \ge 1$ (or equivalently, $T \neq \varnothing$).  Then:
	\begin{enumerate}[(i)]
		\ii Pastures $1$ through $N-1$ contain either nothing or an attached component.
		\ii Pasture $N$ contains nothing if $T[N] = \AA_n[n]$, and contains a single caterpillar otherwise, with color corresponding to $\AA_n[n]$.
	\end{enumerate}
	\label{thm:pasture}
\end{theorem}

\subsection{Proof of the Bubble Lemma}
We begin with a proof of the bubble theorem, which is the crux result of the alternating case.  Indeed, both of the subsequent theorems are fairly straightforward consequences of this theorem.

It's interesting to note that the Bubble Lemma is intuitively very natural.  The main difficulty is finding a clean way to handle the special cases generated by the convoluted geometry.

\begin{proof}[Proof of Lemma \ref{thm:bubble}]
	Take a bubble $B$ and assume without loss of generality that it is blue.  It is easy to see, by considering two anchors on the boundary of blue, that there is some red anchor inside $B$.  This implies that $B$ has at least one red caterpillar.

@@

\subsection{Proof of the Caterpillar Theorem}
We will now derive the Caterpillar Theorem as a consequence of the Bubble Lemma.

@@

	We perform induction on the size of the caterpillar. 
	If there are no bubbles, then the caterpillar is simply a barbell (because it is a tree, which contracts to a barbell).
	This is the base step.
	For the inductive step, consider an arbitrary bubble.  Inside it is exactly one caterpillar, say $c$, by the Bubble Lemma.  Because the original caterpillar has nesting level $0$, we deduce $c$ is merely a barbell, and hence is either $\alpha_s$ or $\alpha_t$.
	Applying the barbell-forcing rule of equation \eqref{eq:barbell_break} generates two terms.  One of them is zero because it creates a new empty bubble. The other is the original diagram with the cycle cut open and the contents removed, multiplied by one of $\left\{ x,y \right\}$.  The inductive hypothesis now applies directly, and this completes the first induction.

@@

		label("$\to$", (7,0));
	\end{asy}
	\caption{In the first diagram, $\ul a = \ul b = 110010$.  In the second, $\ul a' = \ul b' = 110010111$.  Closing the pastures allows us to deduce the Pasture Theorem from the Bubble Lemma.}
	\label{fig:pf_pasture}
\end{figure}
The bubble theorem and the pasture theorem are structurally very similar.  In fact, we will now show a somewhat surprising proof that the Pasture Theorem follows from the Bubble Lemma.
\begin{proof}[Proof of Theorem \ref{thm:pasture}]
	Again, let $T$ denote the top, with length $N$.  In the first case, suppose $T[N] \neq \AA_n[n]$; that is, the last characters of $T$ and $\AA_n$ differ.  Then it must be the case that the rightmost anchor is not part of a fence.
	Now suppose the map arose from $\MM_{\AA_n}(\ul a, \ul b)$.  Let $\ul a'$ be the string formed by appending $N$ $1$'s to $\ul a$, and define $\ul b'$ similarly.  Now consider the map \[ \MM_{\AA_{n+N}} \left( \ul a', \ul b' \right). \]  See figure \ref{fig:pf_pasture} for an example.

	It is easy to verify that the top of this new map is zero.  Now what we have done is enclose the contents of each pasture into bubbles.  The Bubble Lemma tells us that the innermost bubble can have exactly one caterpillar, while the other bubbles must contain only a single caterpillar, which was once a fence.  This implies the Pasture Theorem in the first case.

@@

\begin{definition*}
	We say that two strings $\ul{r_1}$ and $\ul{r_2}$ \emph{agree}, or \emph{agree in $c$} if their last characters are both $c$.
\end{definition*}
\begin{definition*}
	For a binary string $\ul r$, let $\ul r'$ be the string formed by deleting the last bit of $\ul r$.
\end{definition*}

\begin{corollary}
	For any binary strings $\ul a, \ul b \in \BB_n$, if $\MM_{\AA_n} (\ul a, \ul b)$ is nonzero and has top $T$, then for some nonnegative integers $m_x$, $m_y$, $m_s$, and $m_t$, we have 
	\[
		\MM_{\AA_n} (\ul a, \ul b) =
		x^{m_x}y^{m_y}\alpha_s^{m_s}\alpha_t^{m_t} \cdot
		\begin{cases}
			1 & \text{if $T$ and $\AA_n$ agree} \\
			Q_T & \text{otherwise}
		\end{cases}.
	\]
\end{corollary}
\begin{proof}
	This is an immediate consequence of the Caterpillar Theorem and the Pasture Theorem.  Everything in the first pasture is a product of monomials by the Caterpillar Theorem.  If $T$ and $\AA_n$ agree, then the last pasture is empty and hence we obtain the first case.  Otherwise, there is a single caterpillar of color opposite to $T$, and hence after evaluating that caterpillar, we obtain some monomial times a single barbell.  This generates the final $Q_T$ term.
\end{proof}

@@

\begin{proposition}
	Let $n \ge 2$ be an integer.  Suppose $\ul a, \ul b \in \BB_n$ have the same top $T = \Top_{\AA_n} \ul a = \Top_{\AA_n} \ul b$, and further that $\ul a$ and $\ul b$ agree.  Suppose $M_1 = \MM_{\AA_{n-1}} (\ul a', \ul b') \neq 0$.  Then $M = \MM_{\AA_n} (\ul a, \ul b)$ is nonzero, and the following recursion holds.
	\begin{enumerate}[(i)]
		\ii If $\AA_n$ and $T$ have the same last character $c$ (so $T \neq \varnothing$)
		\begin{itemize}
			\ii If $\ul a[n] = \ul b[n] = 1$, then $M = M_1$.
			\ii If $\ul a[n] = \ul b[n] = 0$, then $M = -f / \alpha_k$ where $f$ is the monomial in $M_1$ with the largest factor of $\alpha_k$, with any quantum numbers
		\end{itemize}
	\end{enumerate}
	BLAH BLAH BLAH BLAH BLAH 
	% TODO : figure out what the hell this is supposed to be
	\label{thm:recurse}
\end{proposition}
